---
title: "Basic-Use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic-Use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(depict))
suppressMessages(library(magrittr))
suppressMessages(library(grid))

```

# depict

depict is an R wrapper around the wonderful depiction api written by [John May](https://github.com/johnmay).  The entire [CDK](https://github.com/cdk) team, but especially
John, have been steadily improving the visualization features of CDK. The depiction API is
succinct and powerful and provides access to a vary large amount of the end-user desired functionality with a small number of composable functions. Because of the design of this API
it is now relatively straightforward to design a simple streamlined interface to allow users to quickly and easily generate beautiful graphics.


## Simple Depiciton

A simple wrapper around cdk's excellent depict module.

```{r warning=FALSE, message=FALSE, eval=FALSE}
library(depict)
library(magrittr)
library(grid)

# you must supply java colors 
color <- J("java.awt.Color")

# load in penicillin
pen  <- parse_smiles("CC1(C(N2C(S1)C(C2=O)NC(=O)CC3=CC=CC=C3)C(=O)[O-])C penicillin")
cav  <- parse_smiles("CN1C=NC2=C1C(=O)N(C(=O)N2C)C")

# define the regions to highlight
# either all atoms/bonds
# or a SMARTS-defined subregion
atms <- pen$atoms()
bnds <- pen$bonds()
lactam <- match_smarts("C1(=O)NCC1", pen)

# use piping to change the behavior as desired
depiction() %>%
  highlight_atoms(atms, color$LIGHT_GRAY) %>%
  highlight_atoms(bnds, color$LIGHT_GRAY) %>%
  highlight_atoms(lactam, color$RED) %>%
  set_size(400, 400) %>%
  set_zoom(3) %>%
  outerglow() %>%
  add_title() %>%
  depict(pen) %>%
  get_image() %>%
  grid::grid.raster()


```


## A Larger Example


```{r message=FALSE, eval=FALSE}
insulinmol <- system.file("molfiles/ChEBI_5931.mol", package="depict")
insulin    <- read_mol(insulinmol)

cysteine <- match_smarts("C(=O)C(CS)N", insulin)
xlinks   <- match_smarts("SS", insulin)

depiction()%>% 
  set_size(700, 400) %>%
  set_zoom(10) %>%
  outerglow() %>%
  highlight_atoms(cysteine, color$YELLOW) %>%
  highlight_atoms(xlinks, color$YELLOW) %>%
  depict(insulin)%>%
  get_image() %>%
  grid::grid.raster()

```

# Multiple Smiles

```{r}

atmcontainers <-  purrr::map(
  c("CCCC", "CCCCCC", "CCCC1CCC1CC2CCCC2"),
  parse_smiles)


  
many_containers <- atomcontainer_list_to_jarray(atmcontainers)


#
# here we will depict the collection in a single image
#
depiction() %>%
  depict(many_containers) %>%
  get_image() %>%
  grid::grid.raster()


```

